A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Remaking table
Fixes graph and table

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|}
\hline
Experiment & Median Time & \multicolumn{2}{|c|}{Median IPs} &
\multicolumn{2}{|c|}{Median PUTs} & \#Runs & Different IPs\\
           &   (ms)        & Total & Used & Total & Used &
           &\\
\hline
base & 120056.0 & 10 & 4 & 256.0 & 21.0 & 81 & 262\\
\hline
graph1 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 36 & 96\\
graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 36 & 73\\
\hline
reboot & 796214.0 & 9 & 6 & 646.0 & 67.0 & 45 & 168\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 55 & 225\\
\hline
\end{tabular}
%% Initially generated with this code, 
%% <<experiments, cache=FALSE,echo=FALSE>>=
%% experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%% kable(experiment.aggregates)
%% @ %def

@@

<<zipf, cache=FALSE,echo=FALSE,fig.height=3>>=
ggplot(ips.data,aes(x=idx,y=PUTs,group=Experiment,color=Experiment))+geom_point()+scale_y_log10()+ scale_colour_discrete(labels=c('base','graph1','graph2','reboot','cachereboot'))
@ %def graph for IPs and puts

>>>>

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Experiment & Median Time & \multicolumn{2}{|c|}{Median IPs} &
\multicolumn{3}{|c|}{Median PUTs} & \#Runs & Unique IPs & Puts/IP \\
           &   (ms)        & Total & Used & Total & Used & Ratio &  & & \\
\hline
base & 120056.0 & 10 & 4 & 256.0 & 21.0 & 0.1290323 & 81 & 262 & 21.33333\\
\hline
graph1 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 0.1282238 & 36 & 96 & 24.30000\\

graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 0.0520509 & 36 & 73 & 129.04545\\
\hline
reboot & 796214.0 & 9 & 6 & 646.0 & 67.0 & 0.0955121 & 45 & 168 & 75.88889\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 0.1575092 & 55 & 225 & 43.28571\\
\hline
\end{tabular}
%% \end{tabular}
%% Initially generated with this code, 
% <<experiments, cache=FALSE,echo=FALSE>>=
%experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
%kable(experiment.aggregates)
%@ %def

@@

<<zipf, cache=FALSE,echo=FALSE,fig.height=3>>=
ggplot(ips.data,aes(x=idx,y=PUTs,group=Experiment,color=Experiment))+geom_point()+scale_y_log10()+ scale_colour_discrete(labels=c('base','graph1','graph2','reboot','cachereboot'))+scale_x_log10()
@ %def graph for IPs and puts
